---
title: "UWBiost561"
output: 
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float:
      toc_collapsed: true
    theme: united
vignette: >
  %\VignetteIndexEntry{UWBiost561}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a demo vignette for our package. We will first demonstrate on how to generate a graph with a random partial clique via the `generate_partial_clique()` function, then we will demonstrate how to compute maximal partial cliques via one and also various implementations within this package.

# Generating a graph

The following lines of code runs the  `generate_partial_clique()` function with n = 10, clique_fraction = 0.5, and  clique_edge_density = 0.9. For further detailed documentation, please visit the reference page.

```{r}
library(UWBiost561)
set.seed(0)
simulation <- UWBiost561::generate_partial_clique(
  n = 10,
  clique_fraction = 0.5,
  clique_edge_density = 0.9
)
adj_mat <- simulation$adj_mat
adj_mat
```


# Calculating partial Clique

Now that we generated a graph, we can compute maximal partial cliques via one and also various implementations within this package. The following lines of code will use the default implementation of `compute_maximal_partial_clique()`, which is created by the author directly.


```{r}
set.seed(10)
res <- UWBiost561::compute_maximal_partial_clique(
  adj_mat = adj_mat,
  alpha = 0.9
)
res
```

# Using different implementations for calculating partial Clique

There are also many other implements of `compute_maximal_partial_clique()` within this package, where they can be called directly via `compute_maximal_partial_clique1()` to `compute_maximal_partial_clique15()`, or be call through `compute_maximal_partial_clique_master()` and setting the `number` parameter to the desired implementation. For number 10 of the implementation, it will act exactly the same as the default `compute_maximal_partial_clique()`. We will demonstrate an example on why the master function is useful in the next section. Note: Be warned that not all implementations are the same, some might not return the correct maximal partial clique, and others might fail all together.

```{r}
set.seed(10)
result <- UWBiost561::compute_maximal_partial_clique_master(
  adj_mat = adj_mat, 
  alpha = 0.95, 
  number = 11, 
  time_limit = 30
)
result
```

# Small example simulation testing

Now, the following code will provide a small foundation on how to do simulation testing between all implementations of `compute_maximal_partial_clique()` via the help of master function. This is a very light demo that iterates between different values of n, and also implement error handling just in case for implementations that fails. Since this was a demo, we only ran through 1 trial with 1 n, thus this did not take much time to complete. Be aware that for larger n, the run time will start to increase exponentially, please carefully plan your simulation study and make sure it fits within the computational resources that you have acess to.

```{r}
rm(list=ls())
set.seed(10)
library(UWBiost561)

imp_numbers <- 1:15
trials <- 1
n_numbers <- 6

# Generate the simulation
level_trial_list <- lapply(1:trials, function(trial){
  print(paste("Working on Trial:", trial))
  set.seed(trial)  # Freeze randomness for this trial

  # Loop over the different implementations (imp_numbers)
  trial_result_list <- lapply(imp_numbers, function(imp_number){
    print(paste("Working on Implementation:", imp_number))

    # Loop over n values from 5 to 10 for each implementation
    result_n_list <- lapply(n_numbers, function(n){
      set.seed(trial)  # To freeze the randomness of adj_mat generation
      print(paste("Generating with n =", n))

      # Generate the adjacency matrix with varying n (5 to 10)
      data <- UWBiost561::generate_partial_clique(n = n,
                                                  clique_fraction = 0.5,
                                                  clique_edge_density = 0.95)
      adj_mat <- data$adj_mat

      # Compute the maximal partial clique for this n and imp_number
      result <- tryCatch({
        # Attempt to run the function
        UWBiost561::compute_maximal_partial_clique_master(
          adj_mat = adj_mat,
          alpha = 0.95,
          number = imp_number,
          time_limit = 30
        )
      }, error = function(e) {
        # Handle the error: 'e' will contain the error message
        cat("An error occurred:", e$message, "\n")
        return(NULL)  # Return NULL
      })

      return(result)
    })

    names(result_n_list) <- paste("n =", 10)
    return(result_n_list)
  })

  names(trial_result_list) <- paste("Implementation:", imp_numbers)
  return(trial_result_list)
})

names(level_trial_list) <- paste("Trial:", 1:trials)

level_trial_list
```
